---
title: "Hmisc"
author: "Ryan Atkinson"
date: "5/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

reference: https://rstudio-pubs-static.s3.amazonaws.com/344055_0c737f77c0ef4e36b6865cb843a7bb4a.html#hmisc

# Hmisc

It offers 2 powerful functions for imputing missing values. These are impute() and aregImpute(). Though, it also has transcan() function, but aregImpute() is better to use.

Here are some important highlights of this package:

    It assumes linearity in the variables being predicted.
    Fisher’s optimum scoring method is used for predicting categorical variables.

```{r, echo = FALSE, comment=FALSE}
library(Hmisc)
library(missForest)
library(tidyverse)
#load data
data("iris")

#introduce missing values to the data (10%)
iris_mis <- prodNA(iris, noNA = 0.1)
```

```{r, echo = FALSE } 
#using aregImpute(): multiple imputation

impute_areg <- aregImpute(~ Sepal.Length + Sepal.Width + Petal.Length + Petal.Width + Species, data = iris_mis, n.impute = 5)

# aregImpute() automatically identifies the variable type and treats them accordingly.

impute_areg

# The output shows R² values for predicted missing values. Higher the value, better are the values predicted. You can also check imputed values using the following command

# check imputed variable Sepal.Length
# impute_areg$imputed$Sepal.Length
```

```{r}
# using impute.transcan to create dataset of imputed values
complete_data <- impute.transcan(impute_areg, imputation=1, data=iris_mis, list.out=TRUE,pr=FALSE, check=TRUE) 
```

```{r}
complete_data <- complete_data %>% as_tibble() # turning into tibble will remove asterisks
```




